The title

### 2018-04-12 writeup.Rmd
data collection and plotting

```{r importData, warning=FALSE, echo=FALSE}
data <- read_csv("experiments/pilot/3_processed_data/pilot_data.csv")
data$response <- pilot_data$response %>% tolower()

@@

# high definition only considers the highest point on the scale as "literal"
pragmatic_trials$high<-1
pragmatic_trials[pragmatic_trials$response=="right" | pragmatic_trials$response=="true",]$high <-0

# low definition only considers the lowers point on the scale as implicature 
pragmatic_trials$low<-0
pragmatic_trials[pragmatic_trials$response=="wrong" | pragmatic_trials$response=="false",]$low <-1

@@

100 participants (20 per condition) were recruited using Amazon Mechanical Turk. No participant was excluded from the final analysis.

@@

binary_summary$response <- factor(binary_summary$response, levels = c("wrong","right"))
binary_summary$guess_type <- factor(binary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
binary_summary$guess_type <- recode(binary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

binary_plot<-
  binary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=17)) +
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)

@@

@@

>>>>

```{r importData, warning=FALSE, echo=FALSE}
data <- read_csv("experiments/main/3_processed_data/data_main.csv")

data$response_type <- recode(data$response_type, quatenary = "quaternary", tertiary = "ternary")

@@

# high definition only considers the highest point on the scale as "literal"
pragmatic_trials$high<-1
pragmatic_trials[pragmatic_trials$response=="Right"]$high <-0

# low definition only considers the lowers point on the scale as implicature 
pragmatic_trials$low<-0
pragmatic_trials[pragmatic_trials$response=="Wrong"]$low <-1

@@

```{r participants}
participants_info <-
  data %>%
  group_by(response_type) %>%
  summarise(count = n()/24)
```

200 participants were recruited using Amazon Mechanical Turk (binary=`r participants_info$count[1]`, ternary`r participants_info$count[4]`, quaternary=`r participants_info$count[2]`, quinary=`r participants_info$count[3]`). No participant was excluded from the final analysis.

@@

binary_summary$response <- factor(binary_summary$response, levels = c("Wrong","Right"))
binary_summary$guess_type <- factor(binary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
binary_summary$guess_type <- recode(binary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

binary_plot<-
  binary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=15)) +
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)

@@

```{r ternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}

ternary_summary<-
  data %>%
  filter(response_type=="ternary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), proportion=count/total)

ternary_summary$response <- factor(ternary_summary$response, levels = c("Wrong","Neither", "Right"))
ternary_summary$guess_type <- factor(ternary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
ternary_summary$guess_type <- recode(ternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

ternary_plot<-
  ternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=15)) +
  scale_fill_manual(values = c("red4","grey", "springgreen3"), guide=FALSE)

ternary_plot_g <- ggplot_gtable(ggplot_build(ternary_plot))

strips <- grep("strip-r", ternary_plot_g$layout$name)

ternary_plot_g <- with(ternary_plot_g$layout[strips,],
          gtable_add_grob(ternary_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        
ternary_plot_g$widths[[11]] <- unit(2.5,"cm")

grid.draw(ternary_plot_g)
```

```{r quaternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}

quaternary_summary<-
  data %>%
  filter(response_type=="quaternary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), proportion=count/total)

quaternary_summary$response <- factor(quaternary_summary$response, levels = c("Wrong","Kinda Wrong", "Kinda Right", "Right"))
quaternary_summary$guess_type <- factor(quaternary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
quaternary_summary$guess_type <- recode(quaternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

quaternary_plot<-
  quaternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_manual(values = c("red4", "red3", "springgreen2", "springgreen3"), guide=FALSE)

quaternary_plot_g <- ggplot_gtable(ggplot_build(quaternary_plot))

strips <- grep("strip-r", quaternary_plot_g$layout$name)

quaternary_plot_g <- with(quaternary_plot_g$layout[strips,],
          gtable_add_grob(quaternary_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        
quaternary_plot_g$widths[[11]] <- unit(2.5,"cm")

grid.draw(quaternary_plot_g)
```

```{r quinaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}

quinary_summary<-
  data %>%
  filter(response_type=="quinary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), proportion=count/total)

quinary_summary$response <- factor(quinary_summary$response, levels = c("Wrong","Kinda Wrong", "Neither", "Kinda Right", "Right"))
quinary_summary$guess_type <- factor(quinary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
quinary_summary$guess_type <- recode(quinary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

quinary_plot<-
  quinary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_manual(values = c("red4", "red3", "grey", "springgreen2", "springgreen3"), guide=FALSE)

quinary_plot_g <- ggplot_gtable(ggplot_build(quinary_plot))

strips <- grep("strip-r", quinary_plot_g$layout$name)

quinary_plot_g <- with(quinary_plot_g$layout[strips,],
          gtable_add_grob(quinary_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        
quinary_plot_g$widths[[11]] <- unit(2.5,"cm")

grid.draw(quinary_plot_g)
```

@@

* make sure to break down based on whether participants had logical training or not.
